---
title: "Untitled"
author: '19043'
date: "2020.1.1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Question 

Rewrite an Rcpp function for Exercise 9.4.

Compare the generated random numbers by the two functions using qqplot.

Campare the computation time of the two functions with microbenchmark.

Comments your results.

Exercise9.4: Implement a random walk Metropolis sampler for generating the standard Laplace distribution. For the increment, simulate from a normal distribution. Compare the chains generated when different variances are used for the proposal distribution. Also, compute the acceptance rates of each chain.

## Answer 

```{r}
library(Rcpp)
library(GeneralizedHyperbolic)
library(microbenchmark)
f<-function(x) 0.5*exp(-abs(x))
rwMetropolosR<-function(sigma,x0,N){
  x<-numeric(N)
  x[1]<-x0
  u<-runif(N)
  k<-0
  for (i in 2:N) {
    y<-rnorm(1,x[i-1],sigma)
    if (u[i]<=f(y)/f(x[i-1]))
      x[i]<-y 
    else {
      x[i]<-x[i-1]
      k<-k+1
    }
  }
  return(list(x=x,k=k))
}
cppFunction('NumericVector rwMetropolosC(double sigma, double x0, int N){
  NumericVector x(N+1);
  double k=0;
  x[0]=x0;
  double y=0;
  NumericVector u(N);
  for (int i=0;i<N;i++){
    u[i]=runif(1)[0];
  }
  for (int j=1;j<N-1;j++){
    y=rnorm(1,x[j-1],sigma)[0];
    if (u[j]<=0.5*exp(-abs(y))/(0.5*exp(-abs(x[j-1]))))
      x[j]=y;
    else {
      x[j]=x[j-1];
      k++;
    }
  }
  x[N]=k;
  return x;
}')
set.seed(1)
N<-2000
sigma<-c(.05,.5,2,16)
x0<-25
#rwMetropolosR() returns a list with x and k, with the sample vector and the rejection number. 
rwR1<-rwMetropolosR(sigma[1],x0,N)
rwR2<-rwMetropolosR(sigma[2],x0,N)
rwR3<-rwMetropolosR(sigma[3],x0,N)
rwR4<-rwMetropolosR(sigma[4],x0,N)
#rwMetropolosC() returns a vector x, with the first N the sample and the last the rejection number.
rwC1<-rwMetropolosC(sigma[1],x0,N)
rwC2<-rwMetropolosC(sigma[2],x0,N)
rwC3<-rwMetropolosC(sigma[3],x0,N)
rwC4<-rwMetropolosC(sigma[4],x0,N)
refline <- qskewlap(c(.025, .975))
rwR<-list(rwR1,rwR2,rwR3,rwR4)
rwC<-list(rwC1,rwC2,rwC3,rwC4)
##par(mfrow = c(2, 2))
for (i in 1:4){
  plot(1:2000,rwR[[i]]$x,type = "l",xlab = paste("sigma=",sigma[i]),ylab = "x",main = "Using R codes")
  abline(h=refline)
}
for (i in 1:4) {
  plot(1:2000,rwC[[i]][1:2000],type = "l",xlab = paste("sigma=",sigma[i]),ylab = "x",main = "Using Rcpp")
  abline(h=refline)
}
#acceptance rate with rwMetropolosR
print(c(1-rwR1$k/N,1-rwR2$k/N,1-rwR3$k/N,1-rwR4$k/N))
#acceptance rate with rwMetropolosC
print(c(1-rwC1[N+1]/N,1-rwC2[N+1]/N,1-rwC3[N+1]/N,1-rwC4[N+1]/N))
```

From this, we can see that the samples are close to each other, and their acceptance rates are also similar.

```{r}
#qqplot
a<-ppoints(100)
##par(mfrow = c(2, 2))
for (i in 1:4) {
  QR<-qskewlap(a)
  Q<-quantile(rwR[[i]]$x,a)
  qqplot(QR,Q,main=paste("Using R codes with sigma=",sigma[i]),xlab = "standard Laplace Quantiles",ylab = "Sample Quantiles")
  lines(QR,QR)
}
for (i in 1:4) {
  QR<-qskewlap(a)
  Q<-quantile(rwC[[i]][1:2000],a)
  qqplot(QR,Q,main=paste("Using Rcpp with sigma=",sigma[i]),,xlab = "standard Laplace Quantiles",ylab = "Sample Quantiles")
  lines(QR,QR)
}
```

The figures are similar. However from the figure, we can see when $\sigma=0.5$ or $\sigma=2$, the points are near the lines when the values are small, while those points are a little away from the lines when the values are larger. It is because I set $x_0=25$. If I let $x_0$  be smaller, the points will be closer to the lines.

```{r}
summ<-list(4)
for (i in 1:4) {
  ts<-microbenchmark(rwR[[i]]<-rwMetropolosR(sigma[i],x0,N),rwC[[i]]<-rwMetropolosC(sigma[i],x0,N))
  summ[[i]]<-list(paste0('sigma=',sigma[i]),summary(ts)[,c(1,3,5,6)])
}
print(summ)
```

From this, we can see that Rcpp codes are faster that R codes.