---
title: "Introduction to SC19043"
author: "SC19043"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19043}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

__SC19043__ is a simple R package consisting of two functions, _akde_ and _est.knn_ . The function _akde_ is used to solve is used to solve the adaptive kernel density estimator problem. And the function _est.knn_ is to estimator density with k-Nearest Neighbor method. 

## Benchmarking _akde_ 

The source R code for _akde_ is as follows:
```{r}
akde<-function(x,h,kernel="gaussian"){
  if (kernel=="gaussian")
    K<-function(u)  {(2*pi)^-0.5*exp(-0.5*u^2)}   else if (kernel=="epanechnikov")
    K<-function(u)  {0.75*(1-u^2)*(abs(u)<=1)}   else if (kernel=="triangular")
    K<-function(u)  {(1-abs(u))*(abs(u)<=1)}    else if (kernel=="triweight")
    K<-function(u)  {35/32*(1-u^2)^3*(abs(u)<=1)}   else if (kernel=="biweight")
    K<-function(u)  {15/16*(1-u^2)^2*(abs(u)<=1)}   else if (kernel=="cosine")
    K<-function(u)  {pi/4*cos(pi*u/2)*(abs(u)<=1)}  else 
    return("ERROR in kernel type");
  n<-length(x)
  ah<-h(x)
  fhat<-function(u){
    sum<-0
    for (i in 1:n) {
      sum<-sum+K((u-x[i])/h(u))/h(u)
    }
    return(sum/n)
  }
  return(list(x=x,kernel=kernel,hx=h,h=ah,fhat=fhat))
}
```

Here, we give a example with the data from the normal distribution $N(0,1)$ and the bandwidth function $h(u)=(10+u^4)^{-0.6}$. We just use the guassian kernel then.
```{r}
set.seed(0)
x<-rnorm(2000)
h<-function(u){(10+u^4)^(-0.6)}
fhat<-akde(x,h,kernel = "gaussian")
plot(x,fhat$fhat(x),cex=0.5)
```

## Benchmarking _est.knn_ 

The source R code for _est.knn_ is as follows:
```{r}
library(FNN)
est.knn<-function(x,k){
  n<-length(x)
  x0<-min(x)
  x1<-max(x)
  f_hat<-function(u){
    kx<-knnx.dist(x,u,k=k)[,k]
    return(k/(2*n*kx)*(u<=x1)*(u>=x0))
  }
  return(f_hat)
}
```

Here, we give a example with the data from the normal distribution $N(0,1)$.
```{r}
set.seed(123)
x<-rnorm(1000)
fhat<-est.knn(x,32)
t<-seq(min(x),max(x),length=200)
plot(t,fhat(t),type="l")
```

Actually, we can combine KNN with adaptive KDE. We compute the bandwidths with KNN method. An example is as follow.
```{r}
set.seed(0)
x<-faithful$eruptions
#h<-function(u){knnx.dist(x,u,k=10)[,k]}
fhat<-akde(x,h=function(u){knnx.dist(x,u,k=10)[,10]},kernel = "gaussian")
t<-seq(min(x),max(x),length=100)
plot(t,fhat$fhat(t),type = "l")
```